### 2024-09-09 getting-started.qmd
20240909 - assignment operator

A vector is a series of elements that can be numeric or character.
It has one dimension (length).
To create a vector, use the `c()` to combine elements into a vector:

@@

@@

A data frame has two dimensions: rows and columns.
Here is an example of creating a data frame:

@@

fantasyPoints_weekly = expand.grid(
  ID = 1:12,
  season = c(2022, 2023),
  week = 1:17
)

>>>>

A vector is a series of elements that can be numeric or character.
It has one dimension (length).
To create a vector, use the `c()` to combine elements into a vector.
And, we use the assignment operator (`<-`) to assign the vector to an object named `exampleVector`, so we can access it later.

@@

We can then access the contents of the object by calling its name:

```{r}
exampleVector
```

@@

A data frame has two dimensions: rows and columns.
Here is an example of creating a data frame, while using the assignment operator (`<-`) to assign the data frame to an object so we can access it later:

@@

fantasyPoints_weekly <- expand.grid(
  ID = 1:12,
  season = c(2022, 2023),
  week = 1:17
)
